### 2010-07-21 docs/architecture/architecture.tex
Get rid of edge_nodal_flag
update to show Source/

 The main MAESTRO algorithm files.  Here you will find the main driver,
 the advection routines, etc.

@@

@@

 \item problem directories: {\tt test}, {\tt test2}, {\tt
   test\_spherical}, $\ldots$

@@

  do comp=1,dm
     call multifab_build(umac(n,comp), mla%la(n),1,1, &
                         nodal=edge_nodal_flag(comp,:))
  enddo
\end{verbatim}

>>>>

 The main MAESTRO algorithm directory.  The individual problem directories
 lie under here, and all of the main MAESTRO source lives in the {\tt Source/}
 sub-directory.

@@

 \item {\tt Source}

   The main MAESTRO source.  Here you will find the driver routine, the
   advection routines, etc.  All MAESTRO problems will compile this
   source.

@@

 \item problem directories: {\tt test2}, {\tt
   test\_spherical}, $\ldots$

@@

  do comp=1,dm
     call multifab_build_edge(umac(n,comp), mla%la(n),1,1,comp)
  enddo
\end{verbatim}
